%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\padding}{\vspace{2pt}}
\newcommand{\sectionPadding}{\vspace{4pt}}

\NumTabs{20}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Simon Efremov} & \href{mailto:esemiko@gmail.com}{esemiko@gmail.com}\\
  \textbf{Tech Lead / Software Developer} & +420 604 872 966\\
  \href{https://github.com/esemi}{Github: ~~github.com/esemi} & Prague, Czech Republic\\
  \href{https://www.linkedin.com/in/esemi/}{Linkedin: linkedin.com/in/esemi}\\


\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Summary}
Software Engineer with 14+ years experience in product-oriented companies.
Can set up the development process or be included on ongoing, from scratch to release.
My primary language is Python and comfortable with Rust and Scala.
Interested in data scrapping, graphs and investments.
Best motivated when see the impact on end users.
\sectionPadding

%-----------EXPERIENCE-----------------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Chief Technology Officer}{Remote}
    {Gyre TV}{10/2021 - present}

    \resumeItemListStart
        \resumeItemWithoutTitle{Participating in defining the product roadmap, decomposing new features into tasks, and solving technical challenges.}
        \resumeItemWithoutTitle{Tech: PostgreSQL, Python, FastAPI, React, GitHub Actions, Pytest, asyncio.}
        % \resumeItemWithoutTitle{Tuned the development process: implemented a unified Kanban board with formalised user stories.}
        \resumeItemWithoutTitle{Rebuilt the data collection system: 50x growth in user base and streams.}
        \resumeItemWithoutTitle{Moved part of the infrastructure to another hosting provider: reduced hardware expenses by 30\%.}
        \resumeItemWithoutTitle{Released the first version of the streaming partnership service: from POC to production-ready service.}
    \resumeItemListEnd

    \padding

    \resumeSubheading{Software Developer}{Prague, Czech Republic}
    {Semrush Inc, Sharing Center \& Corporate Access}{01/2022 - present}
    \resumeItemListStart
        \resumeItemWithoutTitle{Develop new features and help to plan the team's half-year horizon roadmap.}
        \resumeItemWithoutTitle{Tech: MongoDB, MySQL, Python, FastAPI, Flask, GRPC, GitLab CI, Pytest, Kubernetes, Helm, GCP.}
        \resumeItemWithoutTitle{Improved the teammates on-boarding process: reviewed documentation and automated manual activities using CI/CD.}
        \resumeItemWithoutTitle{Standardised tasks for integration with other teams: accelerated new integrations.}
        \resumeItemWithoutTitle{Implemented a new access distribution model for corporate clients: made the user experience of the corporate access tool much simpler for 30\% of users.}
    \resumeItemListEnd

    \padding

    \resumeSubheading{Tech Lead}{Prague, Czech Republic}
    {Semrush Inc, Billing Platform}{05/2020 - 12/2021}
    \resumeItemListStart
        \resumeItemWithoutTitle{Tracked the tech goal roadmap, collected requirements for the new subscription system, designed and implement it.}
        \resumeItemWithoutTitle{Tech: PostgreSQL, MySQL, Redis, Python, PHP, FastAPI, Flask, GitLab CI, Pytest, Kubernetes, Helm, GCP.}
        \resumeItemWithoutTitle{Supported a sales model change: designed and implemented the POC of the new SaaS subscription system.}
        \resumeItemWithoutTitle{Migrated the team’s services to the cloud infrastructure: reduced infrastructure expenses by 60\%.}
        \resumeItemWithoutTitle{Supported company expansion: conducted 100+ interviews with candidates for my own and other teams.}
    \resumeItemListEnd

    \padding

    \resumeSubheading{Software Developer}{St. Petersburg, Russia}
    {Various companies, details of previous experience available on request.}{07/2008 - 05/2020}
\resumeSubHeadingListEnd
\sectionPadding

%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeSubItem{Online game bot (Gaming, Automation, \href{https://github.com/esemi/epsilion_wars_mmorpg_automation#the-epsilion-trainer}{link}}{Fully automatic game bot for MMORPG. Tech: Python, Telethon, . (May '23)}
    \padding

    \resumeSubItem{Wellness Mobile App (Mobile, NLP}{Dream analysis application uses natural language processing. Tech: Python, PostgreSQL, FastAPI, nltp, Firebase. (September '22)}
    \padding

    \resumeSubItem{Tax calculator tool (Investing, Taxes, CLI tools, \href{https://github.com/esemi/investments/tree/devel\#investments}{link})}{Used by Czech residents for tax reporting based on Interactive Brokers LLC report. Tech: Python, pandas. (May '22)}
    \padding

    \resumeSubItem{Investment portfolio management tool (Investing, CLI tools)}{Portfolio management software based on reports from five brokerages. Tech: Scala, Javascript, XPath. (April '21)}
    \padding

    \resumeSubItem{Crypto arbitrage bot (Cryptocurrency, Trading)}{The bots looked for exchange rate discrepancies between six cryptocurrency exchanges and made investments accordingly. Tech: Python, Redis, aiohttp, lxml. (June '20)}
    \padding

    \resumeSubItem{Dating face search tool (Crawlers, Search Engine, Face Detection, Face Recognition)}{An automatic analytical system to find Tinder® users by facial image search. Tech: Python, Redis, AWS, OpenCV, Scikit, FFmpeg, (March '19)}
    \padding

    \resumeSubItem{Adult movie data analysis (Crawlers, Visualisation, Graph Theory, Web Services, \href{https://esemi.github.io/pornhub-graph/}{link})}{An interactive graph of pornhub.com clips based on backlinks. Tech: Python, Javascript, lxml, Puppeteer, MongoDB, Sigma.js, Gephi. (July '18)}
    \padding

    \resumeSubItem{Music clustering (Crawlers, Music, Research, \href{https://habr.com/ru/company/semrush/blog/337216/}{link})}{A huge visualisation of the overlap of music styles on Yandex Music (Spotify-like service). Tech: Python, Selenium, lxml, igraph (November '17)}
    \padding

%     \resumeSubItem{Online game bot (Browser Automation, Gaming, \href{https://github.com/esemi/travian-manager\#travian-manager-bot}{link})}{A utility for Travian - an online game - that automates the boring everyday tasks, only reserving the interesting part of the gameplay for the player. Tech: Python, Selenium (Feb. '17)}
%     \padding

%     \resumeSubItem{Online game analytics system(Crawlers, Web Services, Gaming, \href{https://dseye.ru/}{link})}{Collected and displayed metrics for all Destiny Sphere players - an MMORTS game. Tech: PHP, Python, MySQL, Memcached. (January '14)}

\resumeSubHeadingListEnd
\sectionPadding

%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {University of Information Technologies, Mechanic and Optics}{St. Petersburg, Russia}
        {Specialist Degree in Information Systems and Technology (Master’s equivalent)}{09/2006 - 05/2012}
    \resumeSubHeadingListEnd
\sectionPadding

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
	\resumeSubItem{Languages}{\tab\tab Python, SQL, PHP}
	\resumeSubItem{Tools}{\tab\tab\tab\tab FastAPI, Starlette, Flask, Sanic, aiogram, telethon, SQLAlchemy, Selenium, Pytest, Poetry, asyncio, websockets}
	\resumeSubItem{Data}{\tab\tab\tab\tab PostgreSQL, Redis, MySQL, MongoDB, Neo4j}
	\resumeSubItem{Infrastructure}{\tab Kubernetes, Helm, Docker, GCP, GitLab CI/CD, GitHub Actions, Grafana, Splunk}
\resumeSubHeadingListEnd

\end{document}